Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-04 paper/galsize_paper.tex
Finished discussion of previous work

Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, this evidence cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.

>>>>

Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, tension in the level of scatter cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}. This tension is not present in our approach for the reason that the level of scatter is simply a modeling parameter in our approach, and we make no attempt to uncover the physical origin of this scatter. However, our fiducial value choice was motivated by \citet{somerville_etal17}, and in the ongoing follow-up work discussed in \S\ref{subsec:future} we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}.$
